---
title: "Replication File Chapter 2"
author: "Theresa Küntzler"
date: "23 11 2020"
output:
  pdf_document: default
  html_document: default
---

# Packages and Folders
```{r message=FALSE, warning=FALSE}
library(dplyr)
library(caret)
library(purrr)
library(ggplot2)
library(tidyr)
library(pROC)
library(plotROC)

data <- "../data/"

# for plotting
my_lightgreen <- "#74c476"
my_darkgreen <- "#31a354"
my_lightblue <- "#a6cee3"
my_darkblue <- "#1f78b4"
```

# Compare Prototypical Data to Azure
```{r}
load(file = paste0(data, "labdata_azure_emo_max.Rda"))

# extract those with undetected faces: 0: 0% undetected)
labdata_azure_na <- filter(labdata_azure, is.na(emo_anger))
rm(labdata_azure_na)

# confusion matrix
emo_order <- c("neutral", "happy", "angry", "disgust", 
               "surprise", "sad", "fear")
confmat <- confusionMatrix(data = 
                             factor(as.factor(labdata_azure$emo_azure_max_char), 
                                         levels = emo_order),
                           reference = factor(labdata_azure$emotion, 
                                              levels = emo_order),
                           mode = "everything")

confmat

# average sensitivity and precision
mean(data.frame(confmat$byClass)$Sensitivity)
mean(data.frame(confmat$byClass)$Precision, na.rm = T)
rm(confmat)

# confusions as table
emo_order <- c("neutral", "happy", "angry", "disgust", "surprise", "sad", "fear")

## Prop Table
my.prop.tab <- prop.table(table(factor(labdata_azure$emotion, 
                                       levels = emo_order),
                                factor(as.factor(labdata_azure$emo_azure_max_char), 
                                       levels = emo_order)), margin = 1)
my.prop.tab[is.na(my.prop.tab)] <- 0
my.prop.tab

rm(labdata_azure, my.prop.tab, emo_order)
```


# Compare Prototypical Data to Face++
```{r}
load(file = paste0(data, "labdata_facepp_emo_max.Rda"))

labdata_facepp_na <- filter(labdata_facepp, is.na(emo_anger))
rm(labdata_facepp_na)

# confusion matrix
emo_names_fpp <- c("angry", "disgust", "fear", "happy", "neutral", "sad", 
                   "surprise")

confmat <- confusionMatrix(data = 
                             factor(as.factor(labdata_facepp$emo_fpp_max_char), 
                                         levels = emo_names_fpp),
                           reference = factor(labdata_facepp$emotion, 
                                              levels = emo_names_fpp), 
                           mode = "everything")

confmat

# average sensitivity and precision
mean(data.frame(confmat$byClass)$Sensitivity)
mean(data.frame(confmat$byClass)$Precision, na.rm = T)
rm(confmat)

# confusions as table
emo_order_fpp <- c("neutral", "happy", "angry", "disgust", "surprise", "sad", 
                   "fear")

## Prop Table
my.prop.tab <- prop.table(table(factor(labdata_facepp$emotion, 
                                       levels = emo_order_fpp),
                                factor(as.factor(labdata_facepp$emo_fpp_max_char), 
                                       levels = emo_order_fpp)), margin = 1)
my.prop.tab[is.na(my.prop.tab)] <- 0
my.prop.tab

rm(labdata_facepp, my.prop.tab, emo_names_fpp)
```


# Compare Prototypical Data to FaceReader
```{r}
load(file = paste0(data, "labdata_fr.Rda"))

# extract those with undetected faces: 2
labdata_fr_na <- filter(labdata_fr, is.na(Angry))
table(labdata_fr_na$emotion)
rm(labdata_fr_na)

# per category
# angry
1/178*100
# disgust
1/178*100

# images with quality below 0.7
labdata_qual_sm_7 <- filter(labdata_fr, Quality <0.7)
table(labdata_qual_sm_7$emotion)

## all dropout per category (na + below 0.7)
# angry
2/178*100
# digust
2/178*100
# fear
2/178*100
# neutral
1/178*100
# surprise
4/178*100

rm(labdata_qual_sm_7)

# filter quality above 0.7
labdata_fr <- filter(labdata_fr, Quality>0.7)

# confusion matrix
emo_order_fpp <- c("neutral", "happy", "angry", "disgust", "surprise", "sad", 
                   "fear")

confmat <- confusionMatrix(data = factor(as.factor(labdata_fr$emo_fr_max_char), 
                                         levels = emo_order_fpp),
                           reference = factor(labdata_fr$emotion, 
                                              levels = emo_order_fpp),
                           mode = "everything")

confmat

# average sensitivity and precision
mean(data.frame(confmat$byClass)$Sensitivity)
mean(data.frame(confmat$byClass)$Precision, na.rm = T)
rm(confmat)

# confusions as table

## Prop Table
my.prop.tab <- prop.table(table(factor(labdata_fr$emotion, 
                                       levels = emo_order_fpp),
                                factor(as.factor(labdata_fr$emo_fr_max_char), 
                                       levels = emo_order_fpp)), margin = 1)
my.prop.tab[is.na(my.prop.tab)] <- 0
my.prop.tab

rm(labdata_fr, my.prop.tab)
```


# Compare Naturalistic Data to Azure
```{r}
load(file = paste0(data, "sfew_azure_emo_max.Rda"))

# extract those with undetected faces: 282 undetected)
sfew_azure_na <- filter(sfew_azure, is.na(emo_anger))
1- nrow(sfew_azure_na)/1387
table(sfew_azure_na$emotion)/1387*100

# drop out shares
table(sfew_azure_na$emotion)
# drop out shares
table(sfew_azure_na$emotion)
rm(sfew_azure_na)
# % based on amount in category
# anger
64/254
# disgust
21/88
# fear
38/143
# happy
30/270
# neutral
40/236
#sad
62/245
# surprise
27/151

# Confusion Matrix
emo_order <- c("neutral", "happy", "angry", "disgust", "surprise", "sad", "fear")

confmat <- confusionMatrix(data = 
                             factor(as.factor(sfew_azure$emo_azure_max_char), 
                                         levels = emo_order),
                          reference = 
                            factor(sfew_azure$emotion, levels = emo_order),
                          mode = "everything")

confmat

# average sensitivity and precision
mean(data.frame(confmat$byClass)$Sensitivity)
mean(data.frame(confmat$byClass)$Precision, na.rm = T)
rm(confmat)

# confusions as table
## Prop Table
my.prop.tab <- prop.table(table(factor(sfew_azure$emotion, levels = emo_order), 
                factor(as.factor(sfew_azure$emo_azure_max_char), 
                       levels = emo_order)), 
                margin = 1)
my.prop.tab[is.na(my.prop.tab)] <- 0
my.prop.tab

rm(sfew_azure, my.prop.tab)
```


# Compare Naturalistic Data to Face++
```{r}
load(file = paste0(data, "sfew_facepp_emo_max.Rda"))

# extract those with undetected faces
sfew_facepp_na <- filter(sfew_facepp, is.na(emo_anger))
1- (nrow(sfew_facepp_na)/nrow(sfew_facepp))*100
table(sfew_facepp_na$emotion)/1387*100

# drop out shares
table(sfew_facepp_na$emotion)
rm(sfew_facepp_na)
# % based on amount in category
# anger
1/254
# disgust
1/88
# fear
1/143
# happy
2/270
# neutral
0/236
#sad
2/245
# surprise
0/151

# confusion matrix
confmat <- confusionMatrix(data = factor(as.factor(sfew_facepp$emo_fpp_max_char), 
                                         levels = levels(sfew_facepp$emotion)),
                          reference = sfew_facepp$emotion,
                          mode = "everything")

confmat

# average sensitivity and precision
mean(data.frame(confmat$byClass)$Sensitivity)
mean(data.frame(confmat$byClass)$Precision, na.rm = T)
rm(confmat)

# confusions as table
emo_order_fpp <- c("neutral", "happy", "angry", "disgust", "surprise", 
                   "sad", "fear")

## Prop Table
my.prop.tab <- prop.table(table(factor(sfew_facepp$emotion, 
                                       levels = emo_order_fpp), 
                factor(as.factor(sfew_facepp$emo_fpp_max_char), 
                       levels = emo_order_fpp)), 
                margin = 1)
my.prop.tab[is.na(my.prop.tab)] <- 0
my.prop.tab

rm(sfew_facepp, my.prop.tab, emo_order_fpp)
```

# Compare Naturalistic Data to FaceReader
```{r}
load(file = paste0(data, "sfew_fr.Rda"))

# extract those with undetected faces: 750
sfew_fr_na <- filter(sfew_fr, is.na(Angry))
# % detected face
1- length(sfew_fr_na$filename)/length(sfew_fr$filename)
nrow(sfew_fr_na)/nrow(sfew_fr)/1387
table(sfew_fr_na$emotion)

# quality too low
sfew_qual_sm_7 <- filter(sfew_fr, Quality <0.7)
nrow(sfew_qual_sm_7)/nrow(sfew_fr)
table(sfew_qual_sm_7$emotion)/1387
table(sfew_qual_sm_7$emotion)

# sum quality and undetected
# % based on amount in category
# anger
(52+143)/254 * 100
# disgust
(13+48)/88 * 100
# fear
(28+85)/143 * 100
# happy
(54+135)/270 * 100
# neutral
(48+126)/236 * 100
#sad
(48+136)/245 * 100
# surprise
(36+77)/151 * 100

rm(sfew_fr_na, sfew_qual_sm_7)

# keep those with qual >= .7 for the analysis
sfew_fr <- filter(sfew_fr, Quality >=0.7)

# confusion matrix
confmat <- confusionMatrix(data = factor(as.factor(sfew_fr$emo_fr_max_char), 
                                         levels = levels(sfew_fr$emotion)),
                           reference = sfew_fr$emotion, 
                           mode = "everything")

confmat

# average sensitivity and precision
mean(data.frame(confmat$byClass)$Sensitivity)
mean(data.frame(confmat$byClass)$Precision, na.rm = T)
rm(confmat)

rm(sfew_fr)
```

# ROC Curve Analysis

## Prototypical Data
If you wish to replicate the full procedure mark the box with `eval = TRUE' to do the following to: 
1) Create long data frames from the wide ones 
2) Create roc-objects from the long dataframe
3) run the tests
Note, the tests are bootstrapped and therefore stochastic.

You can also jump to loading the test-obejcts reported in the Dissertation
```{r eval=FALSE}
# Prototypical Data Azure
load(file = paste0(data, "labdata_azure_emo_max.Rda"))

labdata_azure_long <- labdata_azure %>%
  select(fullpath, emo_anger, emo_disgust, emo_fear, emo_hapiness, emo_neutral, 
         emo_sadness, emo_surprise, emotion) %>% # select needed variables
  #all except those variables named are observations for long format
  pivot_longer(-c(fullpath, emotion), 
               names_to = "emo_measure",
               values_to = "prediction_prob") %>%
  # create a variable that indicates the true emotion for each images
  mutate(true_emo = case_when(emotion == "angry" & 
                                emo_measure == "emo_anger" ~ 1,
                              emotion == "disgust" & 
                                emo_measure == "emo_disgust" ~ 1,
                              emotion == "fear" & 
                                emo_measure == "emo_fear" ~ 1,
                              emotion == "happy" & 
                                emo_measure == "emo_hapiness" ~ 1,
                              emotion == "neutral" & 
                                emo_measure == "emo_neutral" ~ 1,
                              emotion == "sad" & 
                                emo_measure == "emo_sadness" ~ 1,
                              emotion == "surprise" & 
                                emo_measure == "emo_surprise" ~ 1,
                              TRUE ~ 0))
rm(labdata_azure)

# Prototypical Data Face++
load(file = paste0(data, "labdata_facepp_emo_max.Rda"))

labdata_facepp_long <- labdata_facepp %>%
  select(fullpath, emo_anger, emo_disgust, emo_fear, emo_hapiness, emo_neutral, 
         emo_sadness, emo_surprise, emotion) %>% # select needed variables
  #all except those variables named are observations for long format
  pivot_longer(-c(fullpath, emotion), 
               names_to = "emo_measure",
               values_to = "prediction_prob") %>%
  # create a variable that indicates the true emotion for each images
  mutate(true_emo = case_when(emotion == "angry" & 
                                emo_measure == "emo_anger" ~ 1,
                              emotion == "disgust" & 
                                emo_measure == "emo_disgust" ~ 1,
                              emotion == "fear" & 
                                emo_measure == "emo_fear" ~ 1,
                              emotion == "happy" & 
                                emo_measure == "emo_hapiness" ~ 1,
                              emotion == "neutral" & 
                                emo_measure == "emo_neutral" ~ 1,
                              emotion == "sad" & 
                                emo_measure == "emo_sadness" ~ 1,
                              emotion == "surprise" & 
                                emo_measure == "emo_surprise" ~ 1,
                              TRUE ~ 0))

rm(labdata_facepp)

# Prototypical Data FaceReader
load(file = paste0(data, "labdata_fr.Rda"))

labdata_fr_long <- labdata_fr %>%
  select(Filename2, emotion, Neutral, Happy, Sad, Angry, Surprised, 
         Scared, Disgusted) %>% # select needed variables
  #all except those variables named are observations for long format
  pivot_longer(-c(Filename2, emotion), 
               names_to = "emo_measure",
               values_to = "prediction_prob") %>%
  # create a variable that indicates the true emotion for each images
  mutate(true_emo = case_when(emotion == "angry" & 
                                emo_measure == "Angry" ~ 1,
                              emotion == "disgust" & 
                                emo_measure == "Disgusted" ~ 1,
                              emotion == "fear" & 
                                emo_measure == "Scared" ~ 1,
                              emotion == "happy" & 
                                emo_measure == "Happy" ~ 1,
                              emotion == "neutral" & 
                                emo_measure == "Neutral" ~ 1,
                              emotion == "sad" & 
                                emo_measure == "Sad" ~ 1,
                              emotion == "surprise" & 
                                emo_measure == "Surprised" ~ 1,
                              TRUE ~ 0))


rm(labdata_fr)

# create roc objects
labdata_facepp_roc <- roc(response = labdata_facepp_long$true_emo,
                          predictor = labdata_facepp_long$prediction_prob)

labdata_azure_roc <- roc(response = labdata_azure_long$true_emo,
                         predictor = labdata_azure_long$prediction_prob)

labdata_fr_roc <- roc(response = labdata_fr_long$true_emo,
                      predictor = labdata_fr_long$prediction_prob)

# run the tests

roc_test_lab_facepp_azure <- roc.test(roc1 = labdata_facepp_roc,
                                      roc2 = labdata_azure_roc,
                                      method = "bootstrap")

roc_test_lab_facepp_fr <- roc.test(roc1 = labdata_facepp_roc,
                                   roc2 = labdata_fr_roc,
                                   method = "bootstrap")

roc_test_lab_fr_azure <- roc.test(roc1 = labdata_fr_roc,
                                  roc2 = labdata_azure_roc,
                                  method = "bootstrap")
```

### Loading the test-objects reported in the Dissertation
```{r}
# load the test objects
load(file = paste0(data, "roc_test_lab_facepp_azure.Rda")) # p-value = 0.001253
load(file = paste0(data, "roc_test_lab_facepp_fr.Rda")) # p-value < 2.2e-16
load(file = paste0(data, "roc_test_lab_fr_azure.Rda")) # p-value < 2.2e-16

# inspect them
roc_test_lab_facepp_azure
roc_test_lab_facepp_fr
roc_test_lab_fr_azure

rm(roc_test_lab_facepp_azure, roc_test_lab_facepp_fr, roc_test_lab_fr_azure)
```

## Naturalistic Data

If you wish to replicate the full procedure mark the box with `eval = TRUE' to do the following to: 
1) Create long data frames from the wide ones 
2) Create roc-objects from the long dataframe
3) run the tests
Note, the tests are bootstrapped and therefore stochastic.

You can also jump to loading the test-objects reported in the Dissertation
```{r eval = FALSE}
# Naturalistic Data Azure
load(file = paste0(data, "sfew_azure_emo_max.Rda"))

sfew_azure_long <- sfew_azure %>%
  select(fullpath, emo_anger, emo_disgust, emo_fear, emo_hapiness, emo_neutral, 
         emo_sadness, emo_surprise, emotion) %>% # select needed variables
  #all except those variables named are observations for long format
  pivot_longer(-c(fullpath, emotion), 
               names_to = "emo_measure",
               values_to = "prediction_prob") %>%
  # create a variable that indicates the true emotion for each images
  mutate(true_emo = case_when(emotion == "angry" & 
                                emo_measure == "emo_anger" ~ 1,
                              emotion == "disgust" & 
                                emo_measure == "emo_disgust" ~ 1,
                              emotion == "fear" & 
                                emo_measure == "emo_fear" ~ 1,
                              emotion == "happy" & 
                                emo_measure == "emo_hapiness" ~ 1,
                              emotion == "neutral" & 
                                emo_measure == "emo_neutral" ~ 1,
                              emotion == "sad" & 
                                emo_measure == "emo_sadness" ~ 1,
                              emotion == "surprise" & 
                                emo_measure == "emo_surprise" ~ 1,
                              TRUE ~ 0))

rm(sfew_azure)

# Naturalistic Data Face++
load(file = paste0(data, "sfew_facepp_emo_max.Rda"))

sfew_facepp_long <- sfew_facepp %>%
  select(filepath, emo_anger, emo_disgust, emo_fear, emo_hapiness, emo_neutral, 
         emo_sadness, emo_surprise, emotion) %>% # select needed variables
  #all except those variables named are observations for long format
  pivot_longer(-c(filepath, emotion), 
               names_to = "emo_measure",
               values_to = "prediction_prob") %>%
  # create a variable that indicates the true emotion for each images
  mutate(true_emo = case_when(emotion == "angry" & 
                                emo_measure == "emo_anger" ~ 1,
                              emotion == "disgust" & 
                                emo_measure == "emo_disgust" ~ 1,
                              emotion == "fear" & 
                                emo_measure == "emo_fear" ~ 1,
                              emotion == "happy" & 
                                emo_measure == "emo_hapiness" ~ 1,
                              emotion == "neutral" & 
                                emo_measure == "emo_neutral" ~ 1,
                              emotion == "sad" & 
                                emo_measure == "emo_sadness" ~ 1,
                              emotion == "surprise" & 
                                emo_measure == "emo_surprise" ~ 1,
                              TRUE ~ 0))

rm(sfew_facepp)

# Naturalistic Data FaceReader
load(file = paste0(data, "sfew_fr.Rda"))

sfew_fr_long <- sfew_fr %>%
  select(Filename2, emotion, Neutral, Happy, Sad, Angry, Surprised, Scared, 
         Disgusted) %>% # select needed variables
  #all except those variables named are observations for long format
  pivot_longer(-c(Filename2, emotion), 
               names_to = "emo_measure",
               values_to = "prediction_prob") %>%
  # create a variable that indicates the true emotion for each images
  mutate(true_emo = case_when(emotion == "angry" & 
                                emo_measure == "Angry" ~ 1,
                              emotion == "disgust" & 
                                emo_measure == "Disgusted" ~ 1,
                              emotion == "fear" & 
                                emo_measure == "Scared" ~ 1,
                              emotion == "happy" & 
                                emo_measure == "Happy" ~ 1,
                              emotion == "neutral" & 
                                emo_measure == "Neutral" ~ 1,
                              emotion == "sad" & 
                                emo_measure == "Sad" ~ 1,
                              emotion == "surprise" & 
                                emo_measure == "Surprised" ~ 1,
                              TRUE ~ 0))

rm(sfew_fr)


# create ROC Objects
sfew_facepp_roc <- roc(response = sfew_facepp_long$true_emo,
                       predictor = sfew_facepp_long$prediction_prob)

sfew_azure_roc <- roc(response = sfew_azure_long$true_emo,
                      predictor = sfew_azure_long$prediction_prob)

sfew_fr_roc <- roc(response = sfew_fr_long$true_emo,
                  predictor = sfew_fr_long$prediction_prob)

# run the tests
roc_test_sfew_facepp_azure <- roc.test(roc1 = sfew_facepp_roc,
                                       roc2 = sfew_azure_roc,
                                       method = "bootstrap")

roc_test_sfew_facepp_fr <- roc.test(roc1 = sfew_facepp_roc,
                                    roc2 = sfew_fr_roc,
                                    method = "bootstrap")

roc_test_sfew_fr_azure <- roc.test(roc1 = sfew_fr_roc,
                                   roc2 = sfew_azure_roc,
                                   method = "bootstrap")

```

### Loading the test-objects reported in the Dissertation
```{r}
# load the tests
load(file = paste0(data, "roc_test_sfew_facepp_azure.Rda")) 
load(file = paste0(data, "roc_test_sfew_facepp_fr.Rda")) 
load(file = paste0(data, "roc_test_sfew_fr_azure.Rda")) 

roc_test_sfew_facepp_azure
roc_test_sfew_facepp_fr
roc_test_sfew_fr_azure

rm(roc_test_sfew_facepp_azure, roc_test_sfew_facepp_fr, roc_test_sfew_fr_azure)
```

# Chi-Square Tests for Accuracies
## Prototypical Data
```{r}
# Azure
load(file = paste0(data, "labdata_azure_emo_max.Rda"))
labdata_azure_face_found <- subset(labdata_azure, !is.na(emo_neutral))
# sum of correct images
count_labdata_azure <- sum(labdata_azure_face_found$emo_azure_max_char ==
                             labdata_azure_face_found$emotion)

# Facepp
load(file = paste0(data, "labdata_facepp_emo_max.Rda"))
labdata_facepp_face_found <- subset(labdata_facepp, !is.na(emo_neutral))
count_labdata_facepp <- sum(labdata_facepp_face_found$emo_fpp_max_char ==
                              labdata_facepp_face_found$emotion)

# FaceReader
load(file = paste0(data, "labdata_fr.Rda"))
labdata_fr <- filter(labdata_fr, Quality>0.7)
labdata_fr_face_found <- subset(labdata_fr, !is.na(Neutral))
# sum of correct images
count_labdata_fr <- sum(labdata_fr_face_found$emo_fr_max_char == 
                          labdata_fr_face_found$emotion)

prop.test(x = c(count_labdata_facepp, count_labdata_azure),
          n = c(nrow(labdata_facepp_face_found), nrow(labdata_azure_face_found)))

prop.test(x = c(count_labdata_facepp, count_labdata_fr),
          n = c(nrow(labdata_facepp_face_found), nrow(labdata_fr_face_found)))

prop.test(x = c(count_labdata_fr, count_labdata_azure),
          n = c(nrow(labdata_fr_face_found), nrow(labdata_azure_face_found)))

rm(labdata_azure, labdata_azure_face_found, labdata_facepp, 
   labdata_facepp_face_found, labdata_fr, labdata_fr_face_found, 
   count_labdata_fr, count_labdata_facepp, count_labdata_azure)
```

## Naturalistic Data
```{r}
# Azure
load(file = paste0(data, "sfew_azure_emo_max.Rda"))
sfew_azure_face_found <- subset(sfew_azure, !is.na(emo_neutral))
# sum of correct images
count_sfew_azure <- sum(sfew_azure_face_found$emo_azure_max_char == 
                          sfew_azure_face_found$emotion)

# Facepp
load(file = paste0(data, "sfew_facepp_emo_max.Rda"))
sfew_facepp_face_found <- subset(sfew_facepp, !is.na(emo_neutral))
# sum of correct images
count_sfew_facepp <- sum(sfew_facepp_face_found$emo_fpp_max_char == 
                           sfew_facepp_face_found$emotion)

# FaceReader
load(file = paste0(data, "sfew_fr.Rda"))
sfew_fr <- filter(sfew_fr, Quality>0.7)
sfew_fr_face_found <- subset(sfew_fr, !is.na(Neutral))
# sum of correct images
count_sfew_fr <- sum(sfew_fr_face_found$emo_fr_max_char == 
                       sfew_fr_face_found$emotion)


prop.test(x = c(count_sfew_facepp, count_sfew_azure),
          n = c(nrow(sfew_facepp_face_found), nrow(sfew_azure_face_found)))

prop.test(x = c(count_sfew_facepp, count_sfew_fr),
          n = c(nrow(sfew_facepp_face_found), nrow(sfew_fr_face_found)))

prop.test(x = c(count_sfew_fr, count_sfew_azure),
          n = c(nrow(sfew_fr_face_found), nrow(sfew_azure_face_found)))

rm(sfew_azure, sfew_azure_face_found, sfew_facepp, sfew_facepp_face_found, 
   sfew_fr, sfew_fr_face_found, count_sfew_fr, count_sfew_facepp, 
   count_sfew_azure)
```


-------------------------------------------------------------------------------
# Appendix: Subset of Commonly Recognized Images of Naturalistic Data

## Sensitivity, Precision & Accuracy
### Azure
```{r}
load(file = paste0(data, "sfew_azure_detected_all.Rda"))

emo_order <- c("neutral", "happy", "angry", "disgust", "surprise", "sad", "fear")

confmat <- confusionMatrix(data = 
                             factor(
                               as.factor(sfew_azure_detected_all$emo_azure_max_char), 
                               levels = emo_order),
                          reference = factor(sfew_azure_detected_all$emotion, 
                                             levels = emo_order), 
                           mode = "everything")

confmat

# average sensitivity and precision
mean(data.frame(confmat$byClass)$Sensitivity)
mean(data.frame(confmat$byClass)$Precision, na.rm = T)

rm(confmat, emo_order)
```

### Face++
```{r}
load(file = paste0(data, "sfew_facepp_detected_all.Rda"))

emo_order <- c("neutral", "happy", "angry", "disgust", "surprise", "sad", "fear")

confmat <- confusionMatrix(data = 
                             factor(as.factor(
                               sfew_facepp_detected_all$emo_fpp_max_char), 
                               levels = levels(sfew_facepp_detected_all$emotion)),
                          reference = sfew_facepp_detected_all$emotion, 
                           mode = "everything")

confmat

# average sensitivity and precision
mean(data.frame(confmat$byClass)$Sensitivity)
mean(data.frame(confmat$byClass)$Precision, na.rm = T)

rm(confmat, emo_order)
```

### FaceReader
```{r}
load(file = paste0(data, "sfew_fr_detected_all.Rda"))

confmat <- confusionMatrix(data = 
                             factor(as.factor(sfew_fr_detected_all$emo_fr_max_char), 
                                    levels = levels(sfew_fr_detected_all$emotion)),
                           reference = sfew_fr_detected_all$emotion, 
                           mode = "everything")

confmat

# average sensitivity and precision
mean(data.frame(confmat$byClass)$Sensitivity)
mean(data.frame(confmat$byClass)$Precision, na.rm = T)

rm(confmat)
```


## Chi-Square Tests for Accuracies
```{r}
count_sfew_sample_azure <- sum(sfew_azure_detected_all$emo_azure_max_char ==
                                 sfew_azure_detected_all$emotion)

load(file = paste0(data, "sfew_facepp_detected_all.Rda"))
count_sfew_sample_facepp <- sum(sfew_facepp_detected_all$emo_fpp_max_char ==
                                  sfew_facepp_detected_all$emotion)

load(file = paste0(data, "sfew_fr_detected_all.Rda"))
count_sfew_sample_fr <- sum(sfew_fr_detected_all$emo_fr_max_char == 
                              sfew_fr_detected_all$emotion)

prop.test(x = c(count_sfew_sample_facepp, count_sfew_sample_azure),
          n = c(nrow(sfew_facepp_detected_all), nrow(sfew_azure_detected_all)))

prop.test(x = c(count_sfew_sample_facepp, count_sfew_sample_fr),
          n = c(nrow(sfew_facepp_detected_all), nrow(sfew_fr_detected_all)))

prop.test(x = c(count_sfew_sample_fr, count_sfew_sample_azure),
          n = c(nrow(sfew_fr_detected_all), nrow(sfew_azure_detected_all)))

rm(count_sfew_sample_fr, count_sfew_sample_facepp, count_sfew_sample_azure)
```

## ROC Analysis

If you wish to replicate the full procedure mark the box with `eval = TRUE' to do the following to: 
1) Create long data frames from the wide ones 
2) Create roc-objects from the long dataframe
3) run the tests
Note, the tests are bootstrapped and therefore stochastic.

You can also jump to loading the test-objects reported in the Dissertation
```{r eval = FALSE}
# Azure
sfew_azure_detected_all_long <- sfew_azure_detected_all %>%
  select(fullpath, emo_anger, emo_disgust, emo_fear, emo_hapiness, emo_neutral, 
         emo_sadness, emo_surprise, emotion) %>% # select needed variables
  pivot_longer(-c(fullpath, emotion),
               names_to = "emo_measure",
               values_to = "prediction_prob") %>%
  # create a variable that indicates the true emotion for each images
  mutate(true_emo = case_when(emotion == "angry" & 
                                emo_measure == "emo_anger" ~ 1,
                              emotion == "disgust" & 
                                emo_measure == "emo_disgust" ~ 1,
                              emotion == "fear" & 
                                emo_measure == "emo_fear" ~ 1,
                              emotion == "happy" & 
                                emo_measure == "emo_hapiness" ~ 1,
                              emotion == "neutral" & 
                                emo_measure == "emo_neutral" ~ 1,
                              emotion == "sad" & 
                                emo_measure == "emo_sadness" ~ 1,
                              emotion == "surprise" & 
                                emo_measure == "emo_surprise" ~ 1,
                              TRUE ~ 0))

# Face++
sfew_facepp_detected_all_long <- sfew_facepp_detected_all %>%
  select(filepath, emo_anger, emo_disgust, emo_fear, emo_hapiness, emo_neutral, 
         emo_sadness, emo_surprise, emotion) %>% # select needed variables
  pivot_longer(-c(filepath, emotion), 
               names_to = "emo_measure",
               values_to = "prediction_prob") %>%
  # create a variable that indicates the true emotion for each images
  mutate(true_emo = case_when(emotion == "angry" & 
                                emo_measure == "emo_anger" ~ 1,
                              emotion == "disgust" & 
                                emo_measure == "emo_disgust" ~ 1,
                              emotion == "fear" & 
                                emo_measure == "emo_fear" ~ 1,
                              emotion == "happy" & 
                                emo_measure == "emo_hapiness" ~ 1,
                              emotion == "neutral" & 
                                emo_measure == "emo_neutral" ~ 1,
                              emotion == "sad" & 
                                emo_measure == "emo_sadness" ~ 1,
                              emotion == "surprise" & 
                                emo_measure == "emo_surprise" ~ 1,
                              TRUE ~ 0))

# FaceReader
sfew_fr_detected_all_long <- sfew_fr_detected_all %>%
  select(Filename2, emotion, Neutral, Happy, Sad, Angry, Surprised, Scared, 
         Disgusted) %>% # select needed variables
  pivot_longer(-c(Filename2, emotion), 
               names_to = "emo_measure",
               values_to = "prediction_prob") %>%
  # create a variable that indicates the true emotion for each images
  mutate(true_emo = case_when(emotion == "angry" & emo_measure == "Angry" ~ 1,
                              emotion == "disgust" & 
                                emo_measure == "Disgusted" ~ 1,
                              emotion == "fear" & emo_measure == "Scared" ~ 1,
                              emotion == "happy" & emo_measure == "Happy" ~ 1,
                              emotion == "neutral" & 
                                emo_measure == "Neutral" ~ 1,
                              emotion == "sad" & emo_measure == "Sad" ~ 1,
                              emotion == "surprise" & 
                                emo_measure == "Surprised" ~ 1,
                              TRUE ~ 0))


# create roc objects
sfew_sample_facepp_roc <- roc(response = sfew_facepp_detected_all_long$true_emo,
                       predictor = sfew_facepp_detected_all_long$prediction_prob)

sfew_sample_azure_roc <- roc(response = sfew_azure_detected_all_long$true_emo,
                      predictor = sfew_azure_detected_all_long$prediction_prob)

sfew_sample_fr_roc <- roc(response = sfew_fr_detected_all_long$true_emo,
                  predictor = sfew_fr_detected_all_long$prediction_prob)

# run the tests
#
roc_test_sfew_sample_facepp_azure <- roc.test(roc1 = sfew_sample_facepp_roc,
                                       roc2 = sfew_sample_azure_roc,
                                       method = "bootstrap")

#
roc_test_sfew_sample_facepp_fr <- roc.test(roc1 = sfew_sample_facepp_roc,
                                    roc2 = sfew_sample_fr_roc,
                                    method = "bootstrap")

#
roc_test_sfew_sample_fr_azure <- roc.test(roc1 = sfew_sample_fr_roc,
                                   roc2 = sfew_sample_azure_roc,
                                   method = "bootstrap")
rm(sfew_azure_detected_all_long, sfew_facepp_detected_all_long, 
   sfew_fr_detected_all_long)

rm(sfew_azure_detected_all, sfew_facepp_detected_all, sfew_fr_detected_all)
```

### Loading the test-objects reported in the Dissertation
```{r}
# load the tests
load(file = paste0(data, "roc_test_sfew_sample_facepp_azure.Rda")) 
load(file = paste0(data, "roc_test_sfew_sample_facepp_fr.Rda")) 
load(file = paste0(data, "roc_test_sfew_sample_fr_azure.Rda")) 

roc_test_sfew_sample_facepp_azure
roc_test_sfew_sample_facepp_fr
roc_test_sfew_sample_fr_azure

rm(roc_test_sfew_sample_facepp_azure, roc_test_sfew_sample_facepp_fr, 
   roc_test_sfew_sample_fr_azure)
```


# Appendix: Thresholds

## Compare Prototypical Data to Azure
```{r}
load(file = paste0(data, "labdata_azure_emo_max.Rda"))

# Tresholding
tresholds_labdata_azure <- data.frame(threshold = seq(from = 0, to = 1, 
                                                      by = 0.01),
                                       accuracy = as.numeric(NA),
                                       dropout = as.numeric(NA),
                                       dropout_share = as.numeric(NA))

my_accuracy <- function(threshold) {
  overview_df <- labdata_azure[,c("emo_azure_max_char", "emo_azure_max_value", 
                                  "emotion")] %>%
  mutate(emo_azure_th = case_when(
    emo_azure_max_value >= threshold ~ emo_azure_max_char,
    TRUE ~ NA_character_
  ))
  accuracy <- sum(overview_df$emo_azure_th==overview_df$emotion, na.rm = T)/
    sum(!is.na(overview_df$emo_azure_th))
  return(accuracy)
}

my_dropout <- function(threshold) {
  overview_df <- labdata_azure[,c("emo_azure_max_char", "emo_azure_max_value", 
                                  "emotion")] %>%
  mutate(emo_azure_th = case_when(
    emo_azure_max_value >= threshold ~ emo_azure_max_char,
    TRUE ~ NA_character_
  ))
  dropout <- sum(is.na(overview_df$emo_azure_th))
  return(dropout)
}

my_dropout_share <- function(threshold) {
  overview_df <- labdata_azure[,c("emo_azure_max_char", "emo_azure_max_value", 
                                  "emotion")] %>%
  mutate(emo_azure_th = case_when(
    emo_azure_max_value >= threshold ~ emo_azure_max_char,
    TRUE ~ NA_character_
  ))
  dropout_share <- sum(is.na(overview_df$emo_azure_th))/nrow(overview_df)
  return(dropout_share)
}

tresholds_labdata_azure$accuracy <- unlist(map(.x = 
                                                 tresholds_labdata_azure$threshold, 
                                               .f = my_accuracy))
tresholds_labdata_azure$dropout <- unlist(map(.x = 
                                                tresholds_labdata_azure$threshold, 
                                              .f = my_dropout))
tresholds_labdata_azure$dropout_share <- unlist(
  map(.x = tresholds_labdata_azure$threshold, 
      .f = my_dropout_share))

gather(tresholds_labdata_azure[c("threshold", "dropout_share", "accuracy")], 
       "type", "value", 2:3) %>%
ggplot(data = ., aes(x = threshold, y = value, group = type)) +
  geom_line(aes(linetype = type, color = type)) +
  scale_linetype_manual(name = "Value", values=c("solid", "dotdash"), 
                        labels = c("Accuracy", "Dropout Share")) +
  scale_color_manual(name = "Value", values = c(my_darkgreen, my_darkblue), 
                     labels = c("Accuracy", "Dropout Share")) +
  ylim(0,1) +
  xlab("Threshold") +
  ylab("") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)))

rm(labdata_azure, tresholds_labdata_azure, my_accuracy, 
   my_dropout, my_dropout_share)
```

## Compare Prototypical Data to Face++
```{r}
load(file = paste0(data, "labdata_facepp_emo_max.Rda"))

tresholds_labdata_facepp <- data.frame(threshold = seq(from = 0, to = 1, 
                                                       by = 0.01),
                                       accuracy = as.numeric(NA),
                                       dropout = as.numeric(NA),
                                       dropout_share = as.numeric(NA))

my_accuracy <- function(threshold) {
  overview_df <- labdata_facepp[,c("emo_fpp_max_char", "emo_fpp_max_value", 
                                   "emotion")] %>%
  mutate(emo_fpp_th = case_when(
    emo_fpp_max_value/100 >= threshold ~ emo_fpp_max_char,
    TRUE ~ NA_character_
  ))
  accuracy <- sum(overview_df$emo_fpp_th==overview_df$emotion, na.rm = T)/
    sum(!is.na(overview_df$emo_fpp_th))
  return(accuracy)
}

my_dropout <- function(threshold) {
  overview_df <- labdata_facepp[,c("emo_fpp_max_char", "emo_fpp_max_value", 
                                   "emotion")] %>%
  mutate(emo_fpp_th = case_when(
    emo_fpp_max_value/100 >= threshold ~ emo_fpp_max_char,
    TRUE ~ NA_character_
  ))
  dropout <- sum(is.na(overview_df$emo_fpp_th))
  return(dropout)
}

my_dropout_share <- function(threshold) {
  overview_df <- labdata_facepp[,c("emo_fpp_max_char", "emo_fpp_max_value", 
                                   "emotion")] %>%
  mutate(emo_fpp_th = case_when(
    emo_fpp_max_value/100 >= threshold ~ emo_fpp_max_char,
    TRUE ~ NA_character_
  ))
  dropout_share <- sum(is.na(overview_df$emo_fpp_th))/nrow(overview_df)
  return(dropout_share)
}

tresholds_labdata_facepp$accuracy <- 
  unlist(map(.x = tresholds_labdata_facepp$threshold, 
                                                .f = my_accuracy))
tresholds_labdata_facepp$dropout <- 
  unlist(map(.x = tresholds_labdata_facepp$threshold, 
                                               .f = my_dropout))
tresholds_labdata_facepp$dropout_share <- 
  unlist(map(.x = tresholds_labdata_facepp$threshold, 
                                                     .f = my_dropout_share))

gather(tresholds_labdata_facepp[c("threshold", "dropout_share", "accuracy")], 
       "type", "value", 2:3) %>%
ggplot(data = ., aes(x = threshold, y = value, group = type)) +
  geom_line(aes(linetype = type, color = type)) +
  scale_linetype_manual(name = "Value", values=c("solid", "dotdash"), 
                        labels = c("Accuracy", "Dropout Share")) +
  scale_color_manual(name = "Value", values = c(my_darkgreen, my_darkblue), 
                     labels = c("Accuracy", "Dropout Share")) +
  ylim(0,1) +
  xlab("Threshold") +
  ylab("") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)))

rm(labdata_facepp, tresholds_labdata_facepp, my_accuracy, 
   my_dropout, my_dropout_share)
```

## Compare Prototypical Data to FaceReader
```{r}
load(file = paste0(data, "labdata_fr.Rda"))

tresholds_labdata_fr <- data.frame(threshold = seq(from = 0, to = 1, by = 0.01),
                                       accuracy = as.numeric(NA),
                                       dropout = as.numeric(NA),
                                       dropout_share = as.numeric(NA))

my_accuracy <- function(threshold) {
  overview_df <- labdata_fr[,c("emo_fr_max_char", "emo_fr_max_value", 
                               "emotion")] %>%
  mutate(emo_fr_th = case_when(
    emo_fr_max_value >= threshold ~ emo_fr_max_char,
    TRUE ~ NA_integer_
  ))
  accuracy <- sum(as.character(overview_df$emo_fr_th) == 
                    as.character(overview_df$emotion), na.rm = T)/
    sum(!is.na(overview_df$emo_fr_th))
  return(accuracy)
}

my_dropout <- function(threshold) {
  overview_df <- labdata_fr[,c("emo_fr_max_char", "emo_fr_max_value", 
                               "emotion")] %>%
  mutate(emo_fr_th = case_when(
    emo_fr_max_value >= threshold ~ emo_fr_max_char,
    TRUE ~ NA_integer_
  ))
  dropout <- sum(is.na(overview_df$emo_fr_th))
  return(dropout)
}

my_dropout_share <- function(threshold) {
  overview_df <- labdata_fr[,c("emo_fr_max_char", "emo_fr_max_value", 
                               "emotion")] %>%
  mutate(emo_fr_th = case_when(
    emo_fr_max_value >= threshold ~ emo_fr_max_char,
    TRUE ~ NA_integer_
  ))
  dropout_share <- sum(is.na(overview_df$emo_fr_th))/nrow(overview_df)
  return(dropout_share)
}

tresholds_labdata_fr$accuracy <- unlist(map(.x = tresholds_labdata_fr$threshold,
                                            .f = my_accuracy))
tresholds_labdata_fr$dropout <- unlist(map(.x = tresholds_labdata_fr$threshold, 
                                           .f = my_dropout))
tresholds_labdata_fr$dropout_share <- 
  unlist(map(.x = tresholds_labdata_fr$threshold, 
                                                 .f = my_dropout_share))

gather(tresholds_labdata_fr[c("threshold", "dropout_share", "accuracy")], 
       "type", "value", 2:3) %>%
ggplot(data = ., aes(x = threshold, y = value, group = type)) +
  geom_line(aes(linetype = type, color = type)) +
  scale_linetype_manual(name = "Value", values=c("solid", "dotdash"), 
                        labels = c("Accuracy", "Dropout Share")) +
  scale_color_manual(name = "Value", values = c(my_darkgreen, my_darkblue), 
                     labels = c("Accuracy", "Dropout Share")) +
  ylim(0,1) +
  xlab("Threshold") +
  ylab("") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)))

rm(labdata_fr, tresholds_labdata_fr, my_accuracy, 
   my_dropout, my_dropout_share)
```

## Compare Naturalistic Data to Azure
```{r}
load(file = paste0(data, "sfew_azure_emo_max.Rda"))

tresholds_sfew_azure <- data.frame(threshold = seq(from = 0, to = 1, by = 0.01),
                                       accuracy = as.numeric(NA),
                                       dropout = as.numeric(NA),
                                       dropout_share = as.numeric(NA))

my_accuracy <- function(threshold) {
  overview_df <- sfew_azure[,c("emo_azure_max_char", "emo_azure_max_value", 
                               "emotion")] %>%
  mutate(emo_azure_th = case_when(
    emo_azure_max_value >= threshold ~ emo_azure_max_char,
    TRUE ~ NA_character_
  ))
  accuracy <- sum(overview_df$emo_azure_th==overview_df$emotion, na.rm = T)/
    sum(!is.na(overview_df$emo_azure_th))
  return(accuracy)
}

my_dropout <- function(threshold) {
  overview_df <- sfew_azure[,c("emo_azure_max_char", "emo_azure_max_value", 
                               "emotion")] %>%
  mutate(emo_azure_th = case_when(
    emo_azure_max_value >= threshold ~ emo_azure_max_char,
    TRUE ~ NA_character_
  ))
  dropout <- sum(is.na(overview_df$emo_azure_th))
  return(dropout)
}

my_dropout_share <- function(threshold) {
  overview_df <- sfew_azure[,c("emo_azure_max_char", "emo_azure_max_value", 
                               "emotion")] %>%
  mutate(emo_azure_th = case_when(
    emo_azure_max_value >= threshold ~ emo_azure_max_char,
    TRUE ~ NA_character_
  ))
  dropout_share <- sum(is.na(overview_df$emo_azure_th))/nrow(overview_df)
  return(dropout_share)
}

tresholds_sfew_azure$accuracy <- 
  unlist(map(.x = tresholds_sfew_azure$threshold, .f = my_accuracy))
tresholds_sfew_azure$dropout <- 
  unlist(map(.x = tresholds_sfew_azure$threshold, .f = my_dropout))
tresholds_sfew_azure$dropout_share <- 
  unlist(map(.x = tresholds_sfew_azure$threshold, .f = my_dropout_share))

gather(tresholds_sfew_azure[c("threshold", "dropout_share", "accuracy")], 
       "type", "value", 2:3) %>%
ggplot(data = ., aes(x = threshold, y = value, group = type)) +
  geom_line(aes(linetype = type, color = type)) +
  scale_linetype_manual(name = "Value", values=c("solid", "dotdash"), 
                        labels = c("Accuracy", "Dropout Share")) +
  scale_color_manual(name = "Value", values = c(my_darkgreen, my_darkblue), 
                     labels = c("Accuracy", "Dropout Share")) +
  ylim(0,1) +
  xlab("Threshold") +
  ylab("") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)))

rm(sfew_azure, tresholds_sfew_azure, my_accuracy, 
   my_dropout, my_dropout_share)
```

## Compare Naturalistic Data to Face++
```{r}
load(file = paste0(data, "sfew_facepp_emo_max.Rda"))

tresholds_sfew_facepp <- data.frame(threshold = seq(from = 0, to = 1, by = 0.01),
                                       accuracy = as.numeric(NA),
                                       dropout = as.numeric(NA),
                                       dropout_share = as.numeric(NA))

my_accuracy <- function(threshold) {
  overview_df <- sfew_facepp[,c("emo_fpp_max_char", "emo_fpp_max_value", 
                                "emotion")] %>%
  mutate(emo_fpp_th = case_when(
    emo_fpp_max_value/100 >= threshold ~ emo_fpp_max_char,
    TRUE ~ NA_character_
  ))
  accuracy <- sum(overview_df$emo_fpp_th==overview_df$emotion, na.rm = T)/
    sum(!is.na(overview_df$emo_fpp_th))
  return(accuracy)
}

my_dropout <- function(threshold) {
  overview_df <- sfew_facepp[,c("emo_fpp_max_char", "emo_fpp_max_value", 
                                "emotion")] %>%
  mutate(emo_fpp_th = case_when(
    emo_fpp_max_value/100 >= threshold ~ emo_fpp_max_char,
    TRUE ~ NA_character_
  ))
  dropout <- sum(is.na(overview_df$emo_fpp_th))
  return(dropout)
}

my_dropout_share <- function(threshold) {
  overview_df <- sfew_facepp[,c("emo_fpp_max_char", "emo_fpp_max_value", 
                                "emotion")] %>%
  mutate(emo_fpp_th = case_when(
    emo_fpp_max_value/100 >= threshold ~ emo_fpp_max_char,
    TRUE ~ NA_character_
  ))
  dropout_share <- sum(is.na(overview_df$emo_fpp_th))/nrow(overview_df)
  return(dropout_share)
}

tresholds_sfew_facepp$accuracy <- 
  unlist(map(.x = tresholds_sfew_facepp$threshold, .f = my_accuracy))
tresholds_sfew_facepp$dropout <- 
  unlist(map(.x = tresholds_sfew_facepp$threshold, .f = my_dropout))
tresholds_sfew_facepp$dropout_share <- 
  unlist(map(.x = tresholds_sfew_facepp$threshold, .f = my_dropout_share))

gather(tresholds_sfew_facepp[c("threshold", "dropout_share", "accuracy")], 
       "type", "value", 2:3) %>%
ggplot(data = ., aes(x = threshold, y = value, group = type)) +
  geom_line(aes(linetype = type, color = type)) +
  scale_linetype_manual(name = "Value", values=c("solid", "dotdash"), 
                        labels = c("Accuracy", "Dropout Share")) +
  scale_color_manual(name = "Value", values = c(my_darkgreen, my_darkblue), 
                     labels = c("Accuracy", "Dropout Share")) +
  ylim(0,1) +
  xlab("Threshold") +
  ylab("") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)))

rm(sfew_facepp, tresholds_sfew_facepp, my_accuracy, 
   my_dropout, my_dropout_share)
```

## Compare Naturalistic Data to FaceReader
```{r}
load(file = paste0(data, "sfew_fr.Rda"))

# keep those with qual >= .7 for the analysis
sfew_fr <- filter(sfew_fr, Quality >=0.7)

tresholds_sfew_fr <- data.frame(threshold = seq(from = 0, to = 1, by = 0.01),
                                       accuracy = as.numeric(NA),
                                       dropout = as.numeric(NA),
                                       dropout_share = as.numeric(NA))

my_accuracy <- function(threshold) {
  overview_df <- sfew_fr[,c("emo_fr_max_char", "emo_fr_max_value", 
                            "emotion")] %>%
  mutate(emo_fr_th = case_when(
    emo_fr_max_value >= threshold ~ emo_fr_max_char,
    TRUE ~ NA_integer_
  ))
  accuracy <- sum(overview_df$emo_fr_th==overview_df$emotion, na.rm = T)/
    sum(!is.na(overview_df$emo_fr_th))
  return(accuracy)
}

my_dropout <- function(threshold) {
  overview_df <- sfew_fr[,c("emo_fr_max_char", "emo_fr_max_value", 
                            "emotion")] %>%
  mutate(emo_fr_th = case_when(
    emo_fr_max_value >= threshold ~ emo_fr_max_char,
    TRUE ~ NA_integer_
  ))
  dropout <- sum(is.na(overview_df$emo_fr_th))
  return(dropout)
}

my_dropout_share <- function(threshold) {
  overview_df <- sfew_fr[,c("emo_fr_max_char", "emo_fr_max_value", 
                            "emotion")] %>%
  mutate(emo_fr_th = case_when(
    emo_fr_max_value >= threshold ~ emo_fr_max_char,
    TRUE ~ NA_integer_
  ))
  dropout_share <- sum(is.na(overview_df$emo_fr_th))/nrow(overview_df)
  return(dropout_share)
}

tresholds_sfew_fr$accuracy <- 
  unlist(map(.x = tresholds_sfew_fr$threshold, .f = my_accuracy))
tresholds_sfew_fr$dropout <- 
  unlist(map(.x = tresholds_sfew_fr$threshold, .f = my_dropout))
tresholds_sfew_fr$dropout_share <- 
  unlist(map(.x = tresholds_sfew_fr$threshold, .f = my_dropout_share))

gather(tresholds_sfew_fr[c("threshold", "dropout_share", "accuracy")], 
       "type", "value", 2:3) %>%
ggplot(data = ., aes(x = threshold, y = value, group = type)) +
  geom_line(aes(linetype = type, color = type)) +
  scale_linetype_manual(name = "Value", values=c("solid", "dotdash"), 
                        labels = c("Accuracy", "Dropout Share")) +
  scale_color_manual(name = "Value", values = c(my_darkgreen, my_darkblue), 
                     labels = c("Accuracy", "Dropout Share")) +
  ylim(0,1) +
  xlab("Threshold") +
  ylab("") +
  theme(axis.title.y = element_text(margin = margin(t = 0, r = 15, b = 0, l = 0)),
        axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)))

rm(sfew_fr, tresholds_sfew_fr, my_accuracy, 
   my_dropout, my_dropout_share)

```

# Appendix: Shares on all images

## Compare Prototypical Data to Azure
```{r}
load(file = paste0(data, "labdata_azure_emo_max.Rda"))

## calculate share of correctly identified from all images
table(labdata_azure$emo_azure_max_char)
## 1) all images
sum(labdata_azure$emo_azure_max_char == labdata_azure$emotion, na.rm = T)/1246
round(sum(labdata_azure$emo_azure_max_char == 
            labdata_azure$emotion, na.rm = T)/1246, digits = 2)
## neutral
sum(labdata_azure[labdata_azure$emotion == "neutral",]$emo_azure_max_char ==
      labdata_azure[labdata_azure$emotion == "neutral",]$emotion, na.rm = T)/178
round(sum(labdata_azure[labdata_azure$emotion == "neutral",]$emo_azure_max_char ==
            labdata_azure[labdata_azure$emotion == "neutral",]$emotion, 
          na.rm = T)/178, digits = 2)
## happy
sum(labdata_azure[labdata_azure$emotion == "happy",]$emo_azure_max_char ==
      labdata_azure[labdata_azure$emotion == "happy",]$emotion, na.rm = T)/178
round(sum(labdata_azure[labdata_azure$emotion == "happy",]$emo_azure_max_char ==
            labdata_azure[labdata_azure$emotion == "happy",]$emotion, na.rm = T)
      /178, 
      digits = 2)
## angry
sum(labdata_azure[labdata_azure$emotion == "angry",]$emo_azure_max_char ==
      labdata_azure[labdata_azure$emotion == "angry",]$emotion, na.rm = T)/178
round(sum(labdata_azure[labdata_azure$emotion == "angry",]$emo_azure_max_char ==
            labdata_azure[labdata_azure$emotion == "angry",]$emotion, na.rm = T)/
        178, 
      digits = 2)
## disgust
sum(labdata_azure[labdata_azure$emotion == "disgust",]$emo_azure_max_char ==
      labdata_azure[labdata_azure$emotion == "disgust",]$emotion, na.rm = T)/178
round(sum(labdata_azure[labdata_azure$emotion == "disgust",]$emo_azure_max_char ==
            labdata_azure[labdata_azure$emotion == "disgust",]$emotion, na.rm = T)/
        178, 
      digits = 2)
## surprise
sum(labdata_azure[labdata_azure$emotion == "surprise",]$emo_azure_max_char ==
      labdata_azure[labdata_azure$emotion == "surprise",]$emotion, na.rm = T)/178
round(sum(labdata_azure[labdata_azure$emotion == "surprise",]$emo_azure_max_char ==
            labdata_azure[labdata_azure$emotion == "surprise",]$emotion, 
          na.rm = T)/178, 
      digits = 2)
## sad
sum(labdata_azure[labdata_azure$emotion == "sad",]$emo_azure_max_char ==
      labdata_azure[labdata_azure$emotion == "sad",]$emotion, na.rm = T)/178
round(sum(labdata_azure[labdata_azure$emotion == "sad",]$emo_azure_max_char ==
            labdata_azure[labdata_azure$emotion == "sad",]$emotion, na.rm = T)/
        178, 
      digits = 2)
## fear
sum(labdata_azure[labdata_azure$emotion == "fear",]$emo_azure_max_char ==
      labdata_azure[labdata_azure$emotion == "fear",]$emotion, na.rm = T)/178
round(sum(labdata_azure[labdata_azure$emotion == "fear",]$emo_azure_max_char ==
            labdata_azure[labdata_azure$emotion == "fear",]$emotion, na.rm = T)/
        178, 
      digits = 2)

rm(labdata_azure, confmat)
```


## Compare Prototypical Data to Face++
```{r}
load(file = paste0(data, "labdata_facepp_emo_max.Rda"))
## calculate share of correctly identified from all images
table(labdata_facepp$emo_fpp_max_char)
## 1) all images
sum(labdata_facepp$emo_fpp_max_char == labdata_facepp$emotion, na.rm = T)/1246
round(sum(labdata_facepp$emo_fpp_max_char == labdata_facepp$emotion, na.rm = T)/
        1246, 
      digits = 2)
## neutral
sum(labdata_facepp[labdata_facepp$emotion == "neutral",]$emo_fpp_max_char ==
      labdata_facepp[labdata_facepp$emotion == "neutral",]$emotion, na.rm = T)/178
round(sum(labdata_facepp[labdata_facepp$emotion == "neutral",]$emo_fpp_max_char ==
            labdata_facepp[labdata_facepp$emotion == "neutral",]$emotion, 
          na.rm = T)/178, 
      digits = 2)
## happy
sum(labdata_facepp[labdata_facepp$emotion == "happy",]$emo_fpp_max_char ==
      labdata_facepp[labdata_facepp$emotion == "happy",]$emotion, na.rm = T)/178
round(sum(labdata_facepp[labdata_facepp$emotion == "happy",]$emo_fpp_max_char ==
            labdata_facepp[labdata_facepp$emotion == "happy",]$emotion, 
          na.rm = T)/178, 
      digits = 2)
## angry
sum(labdata_facepp[labdata_facepp$emotion == "angry",]$emo_fpp_max_char ==
      labdata_facepp[labdata_facepp$emotion == "angry",]$emotion, na.rm = T)/178
round(sum(labdata_facepp[labdata_facepp$emotion == "angry",]$emo_fpp_max_char ==
            labdata_facepp[labdata_facepp$emotion == "angry",]$emotion, 
          na.rm = T)/178, 
      digits = 2)
## disgust
sum(labdata_facepp[labdata_facepp$emotion == "disgust",]$emo_fpp_max_char ==
      labdata_facepp[labdata_facepp$emotion == "disgust",]$emotion, na.rm = T)/178
round(sum(labdata_facepp[labdata_facepp$emotion == "disgust",]$emo_fpp_max_char ==
            labdata_facepp[labdata_facepp$emotion == "disgust",]$emotion, 
          na.rm = T)/178, 
      digits = 2)
## surprise
sum(labdata_facepp[labdata_facepp$emotion == "surprise",]$emo_fpp_max_char ==
      labdata_facepp[labdata_facepp$emotion == "surprise",]$emotion, 
    na.rm = T)/178
round(sum(labdata_facepp[labdata_facepp$emotion == "surprise",]$emo_fpp_max_char ==
            labdata_facepp[labdata_facepp$emotion == "surprise",]$emotion, 
          na.rm = T)/178, 
      digits = 2)
## sad
sum(labdata_facepp[labdata_facepp$emotion == "sad",]$emo_fpp_max_char ==
      labdata_facepp[labdata_facepp$emotion == "sad",]$emotion, na.rm = T)/178
round(sum(labdata_facepp[labdata_facepp$emotion == "sad",]$emo_fpp_max_char ==
            labdata_facepp[labdata_facepp$emotion == "sad",]$emotion, 
          na.rm = T)/178, 
      digits = 2)
## fear
sum(labdata_facepp[labdata_facepp$emotion == "fear",]$emo_fpp_max_char ==
      labdata_facepp[labdata_facepp$emotion == "fear",]$emotion, na.rm = T)/178
round(sum(labdata_facepp[labdata_facepp$emotion == "fear",]$emo_fpp_max_char ==
            labdata_facepp[labdata_facepp$emotion == "fear",]$emotion, 
          na.rm = T)/178, 
      digits = 2)

rm(labdata_facepp)
```

## Compare Prototypical Data to FaceReader
```{r}
load(file = paste0(data, "labdata_fr.Rda"))

## calculate share of correctly identified from all images
table(labdata_fr$emo_fr_max_char)
## 1) all images
sum(as.character(labdata_fr$emo_fr_max_char) == labdata_fr$emotion, na.rm = T)/1246
round(sum(as.character(labdata_fr$emo_fr_max_char) == labdata_fr$emotion, 
          na.rm = T)/1246, digits = 2)
## neutral
sum(as.character(labdata_fr[labdata_fr$emotion == "neutral",]$emo_fr_max_char) ==
      labdata_fr[labdata_fr$emotion == "neutral",]$emotion, na.rm = T)/178
round(sum(as.character(labdata_fr[labdata_fr$emotion == "neutral",]$emo_fr_max_char) ==
            labdata_fr[labdata_fr$emotion == "neutral",]$emotion, 
          na.rm = T)/178, 
      digits = 2)
## happy
sum(as.character(labdata_fr[labdata_fr$emotion == "happy",]$emo_fr_max_char) ==
      labdata_fr[labdata_fr$emotion == "happy",]$emotion, na.rm = T)/178
round(sum(as.character(labdata_fr[labdata_fr$emotion == "happy",]$emo_fr_max_char) ==
            labdata_fr[labdata_fr$emotion == "happy",]$emotion, na.rm = T)/178, 
      digits = 2)
## angry
sum(as.character(labdata_fr[labdata_fr$emotion == "angry",]$emo_fr_max_char) ==
      labdata_fr[labdata_fr$emotion == "angry",]$emotion, na.rm = T)/178
round(sum(as.character(labdata_fr[labdata_fr$emotion == "angry",]$emo_fr_max_char) ==
            labdata_fr[labdata_fr$emotion == "angry",]$emotion, na.rm = T)/178, 
      digits = 2)
## disgust
sum(as.character(labdata_fr[labdata_fr$emotion == "disgust",]$emo_fr_max_char) ==
      labdata_fr[labdata_fr$emotion == "disgust",]$emotion, na.rm = T)/178
round(sum(as.character(labdata_fr[labdata_fr$emotion == "disgust",]$emo_fr_max_char) ==
            labdata_fr[labdata_fr$emotion == "disgust",]$emotion, 
          na.rm = T)/178, 
      digits = 2)
## surprise
sum(as.character(labdata_fr[labdata_fr$emotion == "surprise",]$emo_fr_max_char) ==
      labdata_fr[labdata_fr$emotion == "surprise",]$emotion, na.rm = T)/178
round(sum(as.character(labdata_fr[labdata_fr$emotion == "surprise",]$emo_fr_max_char) ==
            labdata_fr[labdata_fr$emotion == "surprise",]$emotion, 
          na.rm = T)/178, 
      digits = 2)
## sad
sum(as.character(labdata_fr[labdata_fr$emotion == "sad",]$emo_fr_max_char) ==
      labdata_fr[labdata_fr$emotion == "sad",]$emotion, na.rm = T)/178
round(sum(as.character(labdata_fr[labdata_fr$emotion == "sad",]$emo_fr_max_char) ==
            labdata_fr[labdata_fr$emotion == "sad",]$emotion, 
          na.rm = T)/178, 
      digits = 2)
## fear
sum(as.character(labdata_fr[labdata_fr$emotion == "fear",]$emo_fr_max_char) ==
      labdata_fr[labdata_fr$emotion == "fear",]$emotion, na.rm = T)/178
round(sum(as.character(labdata_fr[labdata_fr$emotion == "fear",]$emo_fr_max_char) ==
            labdata_fr[labdata_fr$emotion == "fear",]$emotion, 
          na.rm = T)/178, 
      digits = 2)

rm(labdata_fr)
```


## Compare Naturalistic Data to Azure
```{r}
load(file = paste0(data, "sfew_azure_emo_max.Rda"))

## calculate share of correctly identified from all images
table(sfew_azure$emo_azure_max_char)
## 1) all images
round(sum(sfew_azure$emo_azure_max_char == sfew_azure$emotion, na.rm = T)/1387, 
      digits = 2)
## neutral
round(sum(sfew_azure[sfew_azure$emotion == "neutral",]$emo_azure_max_char ==
            sfew_azure[sfew_azure$emotion == "neutral",]$emotion, na.rm = T)/236, 
      digits = 2)
## happy
sum(sfew_azure[sfew_azure$emotion == "happy",]$emo_azure_max_char ==
      sfew_azure[sfew_azure$emotion == "happy",]$emotion, na.rm = T)/270
round(sum(sfew_azure[sfew_azure$emotion == "happy",]$emo_azure_max_char ==
            sfew_azure[sfew_azure$emotion == "happy",]$emotion, na.rm = T)/270, 
      digits = 2)
## angry
sum(sfew_azure[sfew_azure$emotion == "angry",]$emo_azure_max_char ==
      sfew_azure[sfew_azure$emotion == "angry",]$emotion, na.rm = T)/254
round(sum(sfew_azure[sfew_azure$emotion == "angry",]$emo_azure_max_char ==
            sfew_azure[sfew_azure$emotion == "angry",]$emotion, na.rm = T)/254, 
      digits = 2)
## disgust
sum(sfew_azure[sfew_azure$emotion == "disgust",]$emo_azure_max_char ==
      sfew_azure[sfew_azure$emotion == "disgust",]$emotion, na.rm = T)/88
round(sum(sfew_azure[sfew_azure$emotion == "disgust",]$emo_azure_max_char ==
            
            sfew_azure[sfew_azure$emotion == "disgust",]$emotion, na.rm = T)/88, 
      digits = 2)
## surprise
sum(sfew_azure[sfew_azure$emotion == "surprise",]$emo_azure_max_char ==
      sfew_azure[sfew_azure$emotion == "surprise",]$emotion, na.rm = T)/151
round(sum(sfew_azure[sfew_azure$emotion == "surprise",]$emo_azure_max_char ==
            sfew_azure[sfew_azure$emotion == "surprise",]$emotion, 
          na.rm = T)/151, 
      digits = 2)
## sad
sum(sfew_azure[sfew_azure$emotion == "sad",]$emo_azure_max_char ==
      sfew_azure[sfew_azure$emotion == "sad",]$emotion, na.rm = T)/245
round(sum(sfew_azure[sfew_azure$emotion == "sad",]$emo_azure_max_char ==
            sfew_azure[sfew_azure$emotion == "sad",]$emotion, na.rm = T)/245, 
      digits = 2)
## fear
sum(sfew_azure[sfew_azure$emotion == "fear",]$emo_azure_max_char ==
      sfew_azure[sfew_azure$emotion == "fear",]$emotion, na.rm = T)/143
round(sum(sfew_azure[sfew_azure$emotion == "fear",]$emo_azure_max_char ==
            sfew_azure[sfew_azure$emotion == "fear",]$emotion, na.rm = T)/143, 
      digits = 2)

rm(sfew_azure)
```


## Compare Naturalistic Data to Face++
```{r}
load(file = paste0(data, "sfew_facepp_emo_max.Rda"))

## calculate share of correctly identified from all images
table(sfew_facepp$emo_fpp_max_char)
## 1) all images
sum(sfew_facepp$emo_fpp_max_char == sfew_facepp$emotion, na.rm = T)/1387
round(sum(sfew_facepp$emo_fpp_max_char == sfew_facepp$emotion, na.rm = T)/1387, 
      digits = 2)
## neutral
sum(sfew_facepp[sfew_facepp$emotion == "neutral",]$emo_fpp_max_char ==
      sfew_facepp[sfew_facepp$emotion == "neutral",]$emotion, na.rm = T)/236
round(sum(sfew_facepp[sfew_facepp$emotion == "neutral",]$emo_fpp_max_char ==
            sfew_facepp[sfew_facepp$emotion == "neutral",]$emotion, 
          na.rm = T)/236, 
      digits = 2)
## happy
sum(sfew_facepp[sfew_facepp$emotion == "happy",]$emo_fpp_max_char ==
      sfew_facepp[sfew_facepp$emotion == "happy",]$emotion, na.rm = T)/270
round(sum(sfew_facepp[sfew_facepp$emotion == "happy",]$emo_fpp_max_char ==
            sfew_facepp[sfew_facepp$emotion == "happy",]$emotion, 
          na.rm = T)/270, 
      digits = 2)
## angry
sum(sfew_facepp[sfew_facepp$emotion == "angry",]$emo_fpp_max_char ==
      sfew_facepp[sfew_facepp$emotion == "angry",]$emotion, na.rm = T)/254
round(sum(sfew_facepp[sfew_facepp$emotion == "angry",]$emo_fpp_max_char ==
            sfew_facepp[sfew_facepp$emotion == "angry",]$emotion, 
          na.rm = T)/254, 
      digits = 2)
## disgust
sum(sfew_facepp[sfew_facepp$emotion == "disgust",]$emo_fpp_max_char ==
      sfew_facepp[sfew_facepp$emotion == "disgust",]$emotion, na.rm = T)/88
round(sum(sfew_facepp[sfew_facepp$emotion == "disgust",]$emo_fpp_max_char ==
            sfew_facepp[sfew_facepp$emotion == "disgust",]$emotion, 
          na.rm = T)/88, 
      digits = 2)
## surprise
sum(sfew_facepp[sfew_facepp$emotion == "surprise",]$emo_fpp_max_char ==
      sfew_facepp[sfew_facepp$emotion == "surprise",]$emotion, na.rm = T)/151
round(sum(sfew_facepp[sfew_facepp$emotion == "surprise",]$emo_fpp_max_char ==
            sfew_facepp[sfew_facepp$emotion == "surprise",]$emotion, 
          na.rm = T)/151, 
      digits = 2)
## sad
sum(sfew_facepp[sfew_facepp$emotion == "sad",]$emo_fpp_max_char ==
      sfew_facepp[sfew_facepp$emotion == "sad",]$emotion, na.rm = T)/245
round(sum(sfew_facepp[sfew_facepp$emotion == "sad",]$emo_fpp_max_char ==
            sfew_facepp[sfew_facepp$emotion == "sad",]$emotion, 
          na.rm = T)/245, 
      digits = 2)
## fear
sum(sfew_facepp[sfew_facepp$emotion == "fear",]$emo_fpp_max_char ==
      sfew_facepp[sfew_facepp$emotion == "fear",]$emotion, na.rm = T)/143
round(sum(sfew_facepp[sfew_facepp$emotion == "fear",]$emo_fpp_max_char ==
            sfew_facepp[sfew_facepp$emotion == "fear",]$emotion, na.rm = T)/143, 
      digits = 2)

rm(sfew_facepp)
```

## Compare Naturalistic Data to FaceReader
```{r}
load(file = paste0(data, "sfew_fr.Rda"))

# keep those with qual >= .7 for the analysis
sfew_fr <- filter(sfew_fr, Quality >=0.7)

## calculate share of correctly identified from all images
table(sfew_fr$emo_fr_max_char)
## 1) all images
sum(sfew_fr$emo_fr_max_char == sfew_fr$emotion, na.rm = T)/1387
round(sum(sfew_fr$emo_fr_max_char == sfew_fr$emotion, na.rm = T)/1387, 
      digits = 2)
## neutral
sum(sfew_fr[sfew_fr$emotion == "neutral",]$emo_fr_max_char == 
      sfew_fr[sfew_fr$emotion == "neutral",]$emotion, na.rm = T)/236
round(sum(sfew_fr[sfew_fr$emotion == "neutral",]$emo_fr_max_char == 
            sfew_fr[sfew_fr$emotion == "neutral",]$emotion, na.rm = T)/236, 
      digits = 2)
## happy
sum(sfew_fr[sfew_fr$emotion == "happy",]$emo_fr_max_char == 
      sfew_fr[sfew_fr$emotion == "happy",]$emotion, na.rm = T)/270
round(sum(sfew_fr[sfew_fr$emotion == "happy",]$emo_fr_max_char == 
            sfew_fr[sfew_fr$emotion == "happy",]$emotion, na.rm = T)/270, 
      digits = 2)
## angry
sum(sfew_fr[sfew_fr$emotion == "angry",]$emo_fr_max_char == 
      sfew_fr[sfew_fr$emotion == "angry",]$emotion, na.rm = T)/254
round(sum(sfew_fr[sfew_fr$emotion == "angry",]$emo_fr_max_char == 
            sfew_fr[sfew_fr$emotion == "angry",]$emotion, na.rm = T)/254, 
      digits = 2)
## disgust
sum(sfew_fr[sfew_fr$emotion == "disgust",]$emo_fr_max_char == 
      sfew_fr[sfew_fr$emotion == "disgust",]$emotion, na.rm = T)/88
round(sum(sfew_fr[sfew_fr$emotion == "disgust",]$emo_fr_max_char == 
            sfew_fr[sfew_fr$emotion == "disgust",]$emotion, na.rm = T)/88, 
      digits = 2)
## surprise
sum(sfew_fr[sfew_fr$emotion == "surprise",]$emo_fr_max_char == 
      sfew_fr[sfew_fr$emotion == "surprise",]$emotion, na.rm = T)/151
round(sum(sfew_fr[sfew_fr$emotion == "surprise",]$emo_fr_max_char == 
            sfew_fr[sfew_fr$emotion == "surprise",]$emotion, na.rm = T)/151, 
      digits = 2)
## sad
sum(sfew_fr[sfew_fr$emotion == "sad",]$emo_fr_max_char == 
      sfew_fr[sfew_fr$emotion == "sad",]$emotion, na.rm = T)/245
round(sum(sfew_fr[sfew_fr$emotion == "sad",]$emo_fr_max_char == 
            sfew_fr[sfew_fr$emotion == "sad",]$emotion, na.rm = T)/245, 
      digits = 2)
## fear
sum(sfew_fr[sfew_fr$emotion == "fear",]$emo_fr_max_char == 
      sfew_fr[sfew_fr$emotion == "fear",]$emotion, na.rm = T)/143
round(sum(sfew_fr[sfew_fr$emotion == "fear",]$emo_fr_max_char == 
            sfew_fr[sfew_fr$emotion == "fear",]$emotion, na.rm = T)/143, 
      digits = 2)

rm(sfew_fr)
```
