---
title: "Replication File Chapter 3"
author: "Theresa Küntzler"
date: "25 11 2020"
output:
  pdf_document: default
  html_document: default
---

# Packages and Data Preparation
## Packages
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(stringr)
library(brms)
library(data.table)
library(matrixStats)

base_folder <- "../data/"
```

## Load data and Remove Subjects who know the Actor
```{r}
load(file = paste0(base_folder, "subjects_with_emotions_2.Rda"))
#(with subjects who know actor name removed)
load(file = paste0(base_folder, "subjetcs_by_group_no_know_sp.Rda")) 
# one observation: one response time to the four question pages and left-right 
# and feeling therm
load(file = paste0(base_folder, "subjects_rsp.Rda")) 

# table(subjects$know_name_schauspieler)
# remove those from the subjects
subjects <- dplyr::filter(subjects, is.na(know_name_schauspieler))

# remove the same subjects from the rsp_dataset
subjects_rsp <- dplyr::filter(subjects_rsp, subjects_rsp$id %in% subjects$id)
```

## Additional Data Prep
```{r}
# make female dummy (only male and female is used from the gender options):
# gender: 1:weiblich, 2: männlich, 3: divers, 4: keine Angabe
# female: 1 = female, 0 = male
subjects$female <- ifelse(subjects$gender==1, 1, 0)

# Make neutral group the baseline for the emo_char_factor
subjects <- within(subjects, 
                   emotion_group_char_neutral_base <- relevel(
                     as.factor(emotion_group_char), ref = "neutral"))
```

# Treatment Videos on Emotional Reaction of the Subjects (I -> II)
## Emotion Self-Reports by Treatment Group
```{r}
# Scales
summary(lm(aversion ~ emotion_group_char_neutral_base, data = subjects))
summary(lm(fear ~ emotion_group_char_neutral_base, data = subjects))
summary(lm(enthusiasm ~ emotion_group_char_neutral_base, data = subjects))

# Scalte Items
summary(lm(fear_aengstlich/100 ~ emotion_group_char_neutral_base, 
           data = subjects))
summary(lm(fear_besorgnis/100 ~ emotion_group_char_neutral_base, 
           data = subjects))
summary(lm(fear_beunruhigung/100 ~ emotion_group_char_neutral_base, 
           data = subjects)) 
summary(lm(aversion_wut/100 ~ emotion_group_char_neutral_base, 
           data = subjects))
summary(lm(aversion_hass/100 ~ emotion_group_char_neutral_base, 
           data = subjects)) 
summary(lm(aversion_zorn/100 ~ emotion_group_char_neutral_base, 
           data = subjects))
summary(lm(aversion_aufgebracht/100 ~ emotion_group_char_neutral_base, 
           data = subjects)) 
summary(lm(enthusiasm_hoffnung/100 ~ emotion_group_char_neutral_base, 
           data = subjects)) 
summary(lm(enthusiasm_stolz/100 ~ emotion_group_char_neutral_base, 
           data = subjects)) 
summary(lm(enthusiasm_enthusiastisch/100 ~ emotion_group_char_neutral_base, 
           data = subjects))
summary(lm(fear ~ emotion_group_char_neutral_base, data = subjects)) 
summary(lm(aversion ~ emotion_group_char_neutral_base, data = subjects)) 
summary(lm(enthusiasm ~ emotion_group_char_neutral_base, data = subjects))
```

## Emotions in Facial Expressions by Treatment Group
```{r}
# Anger
summary(lm(emo_anger_mean ~ emotion_group_char_neutral_base, 
           data = subjects))
# Fear/Surprise
# add fear and surprise
subjects$emo_fear_surp_mean <- subjects$emo_fear_mean + 
  subjects$emo_surprise_mean
summary(lm(emo_fear_surp_mean ~ emotion_group_char_neutral_base, 
           data = subjects))
```

## Subjects’ Expressions of Anger (Model (3.1))
```{r}
# this loads the model; if you wish to run it: change the filename
anger_mean_brm <- brm(anger_mean ~ 
                        fear_surp_mean_sp + anger_mean_sp + 
                        fear_surp_mean_sp_l2 + anger_mean_sp_l2 + 
                        (1|video_name) + (1|id),
                           data = emo_face_time,
                           control = list(adapt_delta = 0.99),
                           iter = 30000,
                      thin = 3,
                      file = paste0(base_folder, "anger_mean_brm"))

summary(anger_mean_brm)
# plot(anger_mean_brm)
rm(anger_mean_brm)
```

## Subjects’ Expressions of Fear/ Surprise (Model (3.2))
```{r}
# this loads the model; if you wish to run it: change the filename
fear_surp_mean_brm <- brm(fear_surp_mean ~ 
                            fear_surp_mean_sp + anger_mean_sp + 
                            fear_surp_mean_sp_l2 + anger_mean_sp_l2 + 
                            (1|video_name) + (1|id),
                  data = emo_face_time,
                  control = list(adapt_delta = 0.99),
                  iter = 30000,
                  thin = 3,
                  file = paste0(base_folder, "fear_surp_mean_brm"))

summary(fear_surp_mean_brm)
#plot(fear_surp_mean_brm)
rm(fear_surp_mean_brm)
```

# Emotional Reaction on Operating System (II -> III)
## Subjects’ Emotion Self-Reports on Response Time (Model (3.3))
```{r}
# remove single outlier response time
subjects_rsp <- subjects_rsp[subjects_rsp$response_time<=100,]

# add the emo_self_report info to subjects_rsp
subjects_rsp <- left_join(
  x = subjects_rsp,
  y = subjects[,c("fear", "aversion", "enthusiasm", "id", "female", "auth")],
  by = "id"
)

# Model
# this loads the model; if you wish to run it: change the filename
rsp_emo_sr_brm <- brm(
  formula = response_time ~ 
    fear + aversion + enthusiasm + (1|id) + female + auth,
  data = subjects_rsp,
  family = shifted_lognormal(),
  file = paste0(base_folder, "rsp_emo_sr_brm_female_auth")
  ) 

summary(rsp_emo_sr_brm)
#plot(rsp_emo_sr_brm)
rm(rsp_emo_sr_brm)
```

# Operating System on Political Attitude (III -> IV)
```{r}
# calculate response time means
subjects_rsp_mean <- subjects_rsp %>%
  group_by(id) %>%
  summarise(response_time_mean = mean(response_time))

# add response time means to the subjects data
subjects <- left_join(x = subjects, y = subjects_rsp_mean)

# OLS populism on response time, with controls
summary(lm(pop ~ response_time_mean + auth + female, data = subjects))
summary(lm(pop_buergerwillen ~ response_time_mean + auth  + female, 
           data = subjects))
summary(lm(pop_entscheidungen ~ response_time_mean + auth  + female, 
           data = subjects))
summary(lm(pop_unterschiede ~ response_time_mean + auth  + female, 
           data = subjects))
summary(lm(pop_buergervertreter ~ response_time_mean + auth  + female, 
           data = subjects))
summary(lm(pop_reden ~ response_time_mean + auth  + female, data = subjects)) 
summary(lm(pop_kompromiss ~ response_time_mean + auth  + female, 
           data = subjects))

summary(lm(left_right_dist ~ response_time_mean + auth + female, data = subjects))
summary(lm(left_right ~ response_time_mean + auth + female, data = subjects)) 
```

# Populism and Left-Right Self-Placement on Emotion Self-Reports (II -> IV)
```{r}
summary(lm(pop ~ aversion + fear + enthusiasm + auth + female, data = subjects))

summary(lm(pop_buergerwillen ~ aversion + fear + enthusiasm + auth + female, 
           data = subjects)) 
summary(lm(pop_entscheidungen ~ aversion + fear + enthusiasm + auth + female, 
           data = subjects)) 
summary(lm(pop_unterschiede ~ aversion + fear + enthusiasm + auth + female, 
           data = subjects)) 
summary(lm(pop_buergervertreter ~ aversion + fear + enthusiasm + auth + female, 
           data = subjects)) 
summary(lm(pop_reden ~ aversion + fear + enthusiasm + auth + female, 
           data = subjects)) 
summary(lm(pop_kompromiss ~ aversion + fear + enthusiasm + auth + female, 
           data = subjects)) 

summary(lm(left_right_dist ~ aversion + fear + enthusiasm + auth + female, 
           data = subjects))
summary(lm(left_right ~ aversion + fear + enthusiasm + auth + female, 
           data = subjects))
```

# Appendix: Additional Results
## Balance Tests
```{r}
# Table: Female, Authoritarianism, Age and Actor Knowledge on Treatment Groups
summary(lm(female ~ emotion_group_char_neutral_base, data = subjects))
summary(lm(auth ~ emotion_group_char_neutral_base, data = subjects))
summary(lm(age ~ emotion_group_char_neutral_base, data = subjects))
summary(lm(know_politician_schauspieler ~ emotion_group_char_neutral_base, data = subjects))
```

## Treatment Check
```{r}
# Table: Opinion, Competence & Sympathy on Treatment Groups
summary(lm(opinion_schauspieler ~ emotion_group_char_neutral_base, 
           data = subjects))
summary(lm(competence_schauspieler ~ emotion_group_char_neutral_base, 
           data = subjects)) 
summary(lm(sympathy_schauspieler ~ emotion_group_char_neutral_base, 
           data = subjects))
```

## Subjects’ Emotions
```{r}
# Table: Emotion Self-Reports on Treatment Groups
# scale Means
summary(lm(aversion ~ emotion_group_char_neutral_base, data = subjects))
summary(lm(fear ~ emotion_group_char_neutral_base, data = subjects))
summary(lm(enthusiasm ~ emotion_group_char_neutral_base, data = subjects))

# Scale Items
summary(lm(fear_aengstlich/100 ~ emotion_group_char_neutral_base, 
           data = subjects))
summary(lm(fear_besorgnis/100 ~ emotion_group_char_neutral_base, 
           data = subjects)) 
summary(lm(fear_beunruhigung/100 ~ emotion_group_char_neutral_base, 
           data = subjects)) 
summary(lm(aversion_wut/100 ~ emotion_group_char_neutral_base, 
           data = subjects)) 
summary(lm(aversion_hass/100 ~ emotion_group_char_neutral_base, 
           data = subjects)) 
summary(lm(aversion_zorn/100 ~ emotion_group_char_neutral_base, 
           data = subjects)) 
summary(lm(aversion_aufgebracht/100 ~ emotion_group_char_neutral_base, 
           data = subjects))
summary(lm(enthusiasm_hoffnung/100 ~ emotion_group_char_neutral_base, 
           data = subjects))
summary(lm(enthusiasm_stolz/100 ~ emotion_group_char_neutral_base, 
           data = subjects)) 
summary(lm(enthusiasm_enthusiastisch/100 ~ emotion_group_char_neutral_base, 
           data = subjects))
```

```{r}
# Table: Facial Expressions on Treatment Groups : see above: 
# Emotion Self-Reports by Treatment Group

```

## Response Times (Model B.1)
```{r}
# this loads the model; if you wish to run it: change the filename
rsp_times_treatment_brm <- brm(
  response_time ~ question_order_2 + (1|question_type) + (1|emotion_group_char),
  data = subjects_rsp,
  family = shifted_lognormal(),
  control = list(adapt_delta = 0.99),
  file = paste0(base_folder, "rsp_times_brm"))

summary(rsp_times_treatment_brm)
#plot(rsp_times_treatment_brm)
rm(rsp_times_treatment_brm)
```

## Political Attitude
```{r}
# Table: Post Treatment Feeling Thermometer and Left-Right Self-Placement Scores
# on Treatment Groups

# post treatment feeling thermometer ~ treatment group
# only those with feeling thermometer after the treatment
summary(lm(feel_cdu ~ emotion_group_char_neutral_base, 
           data = subjects[subjects$feeling_first==0,]))
summary(lm(feel_csu ~ emotion_group_char_neutral_base, 
           data = subjects[subjects$feeling_first==0,]))
summary(lm(feel_afd ~ emotion_group_char_neutral_base,
           data = subjects[subjects$feeling_first==0,]))
summary(lm(feel_spd ~ emotion_group_char_neutral_base,
           data = subjects[subjects$feeling_first==0,]))
summary(lm(feel_gruene ~ emotion_group_char_neutral_base, 
           data = subjects[subjects$feeling_first==0,]))
summary(lm(feel_linke ~ emotion_group_char_neutral_base, 
           data = subjects[subjects$feeling_first==0,]))


# Post Treatment - Left- Right
# only those with left-right after the treatment
summary(lm(left_right ~ emotion_group_char_neutral_base, 
           data = subjects[subjects$feeling_first==1,]))
summary(lm(left_right_dist ~ emotion_group_char_neutral_base, 
           data = subjects[subjects$feeling_first==1,]))
```

```{r}
# Table: Populism, Elitism & Pluralism on Treatment Groups

# Populism
summary(lm(pop ~ emotion_group_char_neutral_base, data = subjects))
summary(lm(pop_buergerwillen ~ emotion_group_char_neutral_base, 
           data = subjects))
summary(lm(pop_entscheidungen ~ emotion_group_char_neutral_base, 
           data = subjects))
summary(lm(pop_unterschiede ~ emotion_group_char_neutral_base, data = subjects))
summary(lm(pop_buergervertreter ~ emotion_group_char_neutral_base, 
           data = subjects))
summary(lm(pop_reden ~ emotion_group_char_neutral_base, data = subjects))
summary(lm(pop_kompromiss ~ emotion_group_char_neutral_base, data = subjects))

# Elitism
summary(lm(eli ~ emotion_group_char_neutral_base, data = subjects))
summary(lm(eli_anfuehren ~ emotion_group_char_neutral_base, data = subjects))
summary(lm(eli_unternehmer ~ emotion_group_char_neutral_base, data = subjects))
summary(lm(eli_experten ~ emotion_group_char_neutral_base, data = subjects)) 
summary(lm(eli_kampf ~ emotion_group_char_neutral_base, data = subjects)) 

# Pluralism
summary(lm(plu ~ emotion_group_char_neutral_base, data = subjects)) 
summary(lm(plu_kompromiss ~ emotion_group_char_neutral_base, data = subjects))
summary(lm(plu_meinungen ~ emotion_group_char_neutral_base, data = subjects))
```

```{r}
# Table: Elitism & Pluralism on Response Time

# Scale Means
summary(lm(eli ~ response_time_mean + auth + female, data = subjects))
summary(lm(plu ~ response_time_mean + auth + female, data = subjects))

# Scale Items
summary(lm(eli_anfuehren ~ response_time_mean + auth  + female,
           data = subjects))
summary(lm(eli_unternehmer ~ response_time_mean + auth  + female, 
           data = subjects))
summary(lm(eli_experten ~ response_time_mean + auth  + female, data = subjects)) 
summary(lm(eli_kampf ~ response_time_mean + auth  + female, data = subjects))

summary(lm(plu_kompromiss ~ response_time_mean + auth + female, 
           data = subjects))
summary(lm(plu_meinungen ~ response_time_mean + auth+ female, data = subjects))

```

```{r}
# Table: Elitism & Pluralism on Emotion Self-Reports

# Scale Means
summary(lm(eli ~ aversion + fear + enthusiasm + auth + female, data = subjects))
summary(lm(plu ~ aversion + fear + enthusiasm + auth + female, data = subjects))

# Scale Items
summary(lm(eli ~ aversion + fear + enthusiasm + auth + female, data = subjects))
summary(lm(eli_anfuehren ~ aversion + fear + enthusiasm + auth + female, 
           data = subjects))
summary(lm(eli_unternehmer ~ aversion + fear + enthusiasm + auth + female, 
           data = subjects))
summary(lm(eli_experten ~ aversion + fear + enthusiasm + auth + female, 
           data = subjects))
summary(lm(eli_kampf ~ aversion + fear + enthusiasm + auth + female, 
           data = subjects))

summary(lm(plu_kompromiss ~ aversion + fear + enthusiasm + auth + female, 
           data = subjects)) 
summary(lm(plu_meinungen ~ aversion + fear + enthusiasm + auth + female, 
           data = subjects))
```

